\textsf{Are large language models superhuman chemists?}

### 2024-08-31 src/tex/ms.tex
Update ms.tex

    We curated more than 2,500 question-answer pairs, evaluated leading open and closed-source LLMs, and found that, on average, the best models outperformed the chemists. 
    The models, however, struggle with some chemical reasoning tasks that are easy for the human experts and provide overconfident, misleading predictions, such as about chemicals' safety profiles. 
    Although LLMs demonstrate remarkable proficiency in chemical tasks, further research is critical to enhancing their safety and utility in chemical sciences.
\end{abstract}

>>>>

    We curated more than 2,800 question-answer pairs, evaluated leading open and closed-source LLMs, and found that, on average, the best models outperformed the chemists. 
    The models, however, struggle with some chemical reasoning tasks that are easy for the human experts and provide overconfident, misleading predictions, such as about chemicals' safety profiles. 
    Although LLMs demonstrate remarkable proficiency in chemical tasks, further research is critical to enhancing their safety and utility in chemical sciences.
\end{abstract}
